How do domestic GDP growth, global economic conditions, and financial crises impact the export growth rate in different countries?

### 2024-04-19 paper/paper.qmd
new change

---
title: "Deciphering the Temporal Patterns of COVID-19: A Comprehensive Analysis of Case Rates in England"
author: "Mohammed Yusuf Shaikh"
thanks: "Code and data are available at: https://github.com/Yusuf365/Data-Analysis-Regression.git"
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
bibliography: references.bib
---

@@

kable(head(data)[, 2:24])
```

>>>>

---
title: "How do domestic GDP growth, global economic conditions, and financial crises impact the export growth rate in different countries?"
author: "Mohammed Yusuf Shaikh"
thanks: "Code and data are available at: https://github.com/Yusuf365/Data-Analysis-Regression.git"
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
bibliography: references.bib
---

@@

kable(head(data))
```
